---
title: "Advertising vs Revenue - SOLRush"
output:
  pdf_document: default
  html_document: default
date: "2024-10-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Visualize distribution of advertising cost
```{r echo=FALSE, warning=FALSE}
# Main Script: Sales Analysis and Linear Regression
# This script analyzes the relationship between advertising costs and revenue
# using linear regression. It includes data preprocessing, visualization,
# and model creation.

# Load required libraries
library(readxl)
library(ggplot2)
library(imputeTS)
library(caTools)

# Read and preprocess the dataset
dataset <- read_xlsx('sales.xlsx')
dataset <- dataset[2:3]  # Select only columns 2 and 3

# Visualize the distribution of advertising cost and revenue
ggplot(data = dataset, aes(x = advert_cost)) +
  geom_density()
```

### Visualize distribution of  revenue
```{r echo=FALSE, warning=FALSE}
ggplot(data = dataset, aes(x = revenue)) +
  geom_density()
```

### Simple Linear Regression Results
```{r echo=FALSE}
# Impute missing values with mean
dataset$advert_cost <- na_mean(dataset$advert_cost)
dataset$revenue <- na_mean(dataset$revenue)

# Split the dataset into training and testing sets
set.seed(456)
split <- sample.split(dataset$advert_cost, SplitRatio = 4/5)
training_set <- subset(dataset, split == TRUE)
testing_set <- subset(dataset, split == FALSE)

# Create and summarize the linear regression model
linear_model <- lm(formula = revenue ~ advert_cost, data = training_set)
summary(linear_model)
```

## Conclusion

-   Strong correlation between advertising and revenue:Our model shows a remarkably strong relationship between advertising spend and revenue generation. With an R-squared value of 0.9135, we can confidently say that over 91% of the variation in revenue is explained by advertising costs. This is an exceptionally high correlation for a new product, indicating that our marketing efforts are hitting the mark.

-   Significant return on advertising investment: The model suggests that for every dollar spent on advertising, we're generating approximately \$4.42 in revenue (coefficient of 4.4150). This is an impressive return on investment, especially for a new product. It indicates that our advertising strategy is not just effective, but highly efficient in converting spend to sales.

-   Reliable baseline revenue: Even without advertising, the model predicts a baseline revenue of about \$491.50 (intercept value). This suggests our product has inherent appeal or we have effective non-advertising channels driving sales. It's a solid foundation to build upon.

-   Statistical confidence: With p-values well below 0.001 for both the intercept and advertising cost coefficient, we can be extremely confident in these results. They're not just chance findings.


### Visualize representation of linear regression model on the training set
```{r echo=FALSE}
# Visualize the linear regression model on the training set
ggplot() +
  geom_point(aes(x = training_set$advert_cost, y = training_set$revenue), color = 'blue') +
  geom_line(aes(x = training_set$advert_cost, y = predict(linear_model, newdata = training_set)),
            color = 'red') +
  ggtitle('Revenue vs Advertising Cost - Training Set') +
  xlab('Advertising Cost') +
  ylab('Revenue') +
  theme_minimal()
```


# Visualize plot of the linear regression model on the testing set
```{r echo=FALSE}
# Visualize the linear regression model on the testing set
ggplot() +
  geom_point(aes(x = testing_set$advert_cost, y = testing_set$revenue), color = 'black') +
  geom_line(aes(x = training_set$advert_cost, y = predict(linear_model, newdata = training_set)),
            color = 'blue') +
  ggtitle('Revenue vs Advertising Cost - Test Set') +
  xlab('Advertising Cost') +
  ylab('Revenue') +
  theme_minimal()
```

## Recommendations

-   Accelerate advertising spend:Given the strong ROI, I recommend significantly increasing our advertising budget. Every dollar we're not spending on ads is potentially \$3.42 in unrealized profit. We should aggressively scale up our most effective advertising channels.
-   Maintain marketing mix:Whatever blend of advertising channels we're using, it's working exceptionally well. Let's document our current strategy meticulously and use it as a blueprint for future product launches.
-   Explore economies of scale:With such a strong response to advertising, we should investigate bulk media buys or longer-term advertising contracts. This could potentially lower our per-unit advertising costs and further improve our ROI.
-   Set ambitious sales targets:The model suggests our product has significant growth potential. Let's set aggressive sales targets and build out the supply chain and distribution networks to support rapid scaling.
